\begin{center}
\textbf{\large{Abstract}	}
\end{center}

\addcontentsline{toc}{chapter}{Abstract}
\begin{small}

\textbf{Abstract}:

Rust has become an incredibly prominent and widely-used programming language in recent years.
Thanks to its outstanding features of ensuring memory safety and superior performance, the source code of thousands of projects worldwide has been rewritten or newly developed using Rust, from embedded systems to modern web applications.
Rust has been chosen as the development language for enterprise-level projects such as Servo, the web engine of the Mozilla browser, part of the Windows 11 operating system, and many other projects.

These projects demonstrate that Rust is not just a trend but a language with long-term potential for development.
As Rust becomes more popular, the demand for source code analysis, testing, and security tools is also increasing.
When major projects switch to using Rust, ensuring that the source code is safe and error-free becomes a challenge.
However, the current ecosystem and tools for Rust source code analysis are still insufficient.
Since Rust has only become widely used in recent years, the development of analysis tools is still in its early stages.
To enhance the reliability of source code, automated software testing methods are receiving widespread attention and are being widely applied in both the research community and software companies.
One of the methods used in testing is source code analysis or static analysis.
This process involves analyzing, evaluating the quality of the source code, and identifying programming errors and security vulnerabilities without needing to execute the program.

This thesis presents a method for building a source code analysis tool for the Rust language.
The tool's input is Rust source code files, and the output is a Code Property Graph (CPG).
The tool utilizes the Code Property Graph following the specification and existing platform of Joern.
The output can be stored in a graph database, visualized, queried, manually or automatically analyzed to serve various source code analysis purposes.
Additionally, this CPG can be applied to machine learning techniques to detect security vulnerabilities such as graph neural networks (GNN).

\vspace*{1cm}
\textbf{Keywords}: Source code analysis, static analysis, Rust programming language
\end{small}